### 2022-06-01 main/chapter_2ljets.tex
add region def plots; add high figure

\subsection{High}
\label{sec:2ljets_high}
Table~\ref{tab:2ljets_high}.

@@

Figure~\ref{fig:2ljets_high_mll_b}

@@

>>>>

\subsection{High}
\label{sec:2ljets_high}
Table~\ref{tab:2ljets_high}
Figure~\ref{fig:2ljets_high_mll_b}
Figure~\ref{fig:2ljets_high_region}

@@

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh8.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRHigh16.png}
\caption{}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHigh.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRHighR.png}
\caption{}
\end{subfigure}
\caption{%
\TODO{caption}
}
\label{fig:2ljets_high_region}
\end{figure}
